Weak interspecific interactions in a sagebrush steppe: evidence from observations, models, and experiments

### 2017-04-20 removals/manuscript/removal_ms.tex
More revisions (formatting appendices)

\section*{Summary}

\begin{enumerate}
\item A previous study of four dominant species from a sagebrush steppe community used historical data sets and multispecies population models to demonstrate weak interspecific interactions. The models predict little competitive release following species removals.
\item We conducted a removal experiment to test this prediction. We established new quadrats in the same location where the historical data were collected. We assigned half the new quadrats to a  perennial grass removal treatment and half to a treatment in which we removed the dominant shrub, \textit{Artemisia tripartita}. We modeled survival, growth and recruitment as functions of local neighborhood species composition along with an indicator variable for removal treatment. If our ``baseline" model, which accounts for local plant-plant interactions, explains responses to removal, then the fitted removal indicator effect should be non-signficant.
\item  For survival and recruitment, the removal treatment effects were never significantly positive, indicating that competitive release was not underestimated by the interspecific effects included in the baseline model. For  \textit{Poa secunda} recruitment, the removal treatment was actually negative, indicating that our baseline model overestimated competitive release.
\item For growth, the removal treatment effect was significant and positive for two species, \textit{Poa secunda} and \textit{Pseudoroegneria spicata}, indicating that the baseline model underestimated competitive release. However, including information about the location of these grass individuals with respect to removed \textit{A. tripartita} failed to improve the growth regressions, raising questions about the mechanisms driving the positive response to removal.
\item For three species, individual based models and integral projections models based on the vital rate regressions showed that removal treatment effects had little impact on population growth rates or simulated equilibrium cover following a species removal. For \textit{P. spicata}, the population models that included effects of \textit{A. tripartita} removal projected greater competitive release than the baseline models. 
\item \emph{Synthesis}: Although models based on observational data did not perfectly predict species responses to removal, the experimental results increase our confidence that competitive release is in fact small for at least three of our four study species. The implication is that interspecific resource competition is not a primary factor determining the dynamics of this community. The success of the models also supports the use of multispecies models, based on long-term observational studies, to characterize competitive interactions in a community.

\end{enumerate}

@@

Stable coexistence requires that intraspecific interactions must limit populations more than interspecific interactions \citep{chesson_mechanisms_2000}.  Whenever we study populations of species that appear to be coexisting stably, such as populations that have co-occurred in close proximity for extended periods, we should expect intraspecific limitations to be stronger than interspecific limitations. However, we still might expect interspecific interactions to be strong and negative. In fact, plant community ecologists often motivate research on coexistence by noting that all plant species compete for water, light, and a few mineral resources (e.g. \citealt{silvertown_plant_2004}). Resource competition plays a central role in both Tilman's mechanistic resource competition models \citep{tilman_resource_1982} and Grime's Competitor-Stress tolerator-Ruderal strategies \citep{grime_plant_1979}. Neutral theory \citep{hubbell_unified_2001} goes even further, assuming that interspecific competition is exactly as strong as intraspecific competition. A growing list of studies has emphasized the role of interspecific facilitation in some plant communities \citep{he_global_2013,brooker_facilitation_2008}, but it is unclear whether this research has overturned the default assumption that plants compete intensely with other species.

@@

An alternative approach to studying competitive release is to fit multispecies population models that estimate species interactions using long-term, observational data, and then simulate population responses to removals. Applying this approach to arid and semiarid plant communities, we found evidence of strong intraspecific limitation and very weak interspecific interactions, leading to very stable coexistence and implying little competitive release \citep{adler_coexistence_2010,chu_large_2015}. Since we only studied the most common, co-occurring species, we expected to find evidence of stable coexistence, but we were surprised that interspecific interactions and population responses to the loss of dominant species were so weak. Compared to traditional field experiments, our approach has the advantage of projecting full life-cycle responses over long time periods, but its reliance on observational data sets limits the strength of our inference. We would have more confidence in our results if they were confirmed by an experiment.

To test whether our models, which are based on observational data, underestimate the strength of interspecific competition and competitive release, we conducted a removal experiment in a sagebrush steppe. We studied the responses of three perennial grass species to removal of sagebrush, and the response of sagebrush to removal of all grasses. We addressed two research questions: First, are the survival, growth or recruitment of our target species significantly different in control vs. removal treatments after accounting for differences in local species composition? Because our demographic models include the effects of neighborhood crowding, they should be able to predict how experimental removal of neighbors alters demographic performance. If the full effect of experimental removals is stronger than predicted, it means that our statistical models underestimate competitive release.  Our second question integrates across the full life cycle: how do short and long-term population-level responses to removals compare to projections from multispecies population models based on observational data? If models based on observational data adequately predict competitive release, the population dynamics they project should be similar to projections from models that include information from the experimental removal treatments, a result which would validate the use of models and long-term data sets to study interspecific interactions.

@@

Although the primary focus of our analysis is comparison of observed removal responses with responses predicted by our population models, we also conducted a more traditional statistical analysis of differences in cover trends on control vs. removal plots. The response variable for this analysis was year-to-year change in cover at the quadrat scale, calculated as $log(Cover_{t+1}/Cover_t)$. We tested for the effect of removal treatment on this measure of cover change with a linear mixed effects model implemented in the \texttt{lme4} package \citep{Bates2015} of R, including year and quadrat as random effects. We considered the removal treatment effect to be significant when the 95\% confidence interval on the estimated coefficient did not overlap zero.

@@

Our regression models for survival, growth and recruitment follow previous work \citep{adler_coexistence_2010,chu_large_2015}. We model the survival probability of an individual genet as a function of genet size, the neighborhood-scale crowding experienced by the genet from both conspecific and heterospecific genets, temporal variation among years, and permanent spatial variation among groups of quadrats (`group'; here means a set of nearby quadrats located within one pasture or grazing exclosure). Where the current analysis departs from previous work is the inclusion of a categorical removal treatment effect. If the conspecific and heterospecific crowding effects explain demographic rates in removal treatment plots as well as they do in control plots, then there will be no need for the removal treatment effect, and the estimated coefficient will be small and not significantly different from zero. However, if demographic rates in removal plots differ from control plots even after accounting for crowding effects, then the removal treatment effect will be significant. For example, we might find that, holding crowding constant, grasses grow more quickly in the removal plots than in the control plots. This result would indicate that our ``baseline model'', a model including all estimated parameters except for the removal treatment effect, underestimates competitive release. We refer to the model that includes the estimated removal treatment effect as the ``removal model".

Formally, we modeled the survival probability, $S$, of genet $i$ in species $j$ (which is in quadrat group $g$ and removal treatment $h$), 
from time $t$ to $t+1$  as
\begin{equation}
\mbox{logit}(S_{ij,t+1}) = \gamma_{j,t}^S + \varphi_{jg}^S+  \chi_{jh}^S  + \beta_{j,t}^S u_{ij,t} +  
\sum \limits_{m} \omega_{jm}^S {W}_{ijm,t}
\label{eqn:survReg}
\end{equation}
where $\gamma$ is a time-dependent intercept (year effect), $\varphi$ is the coefficient for the 
effect of spatial location group, $\chi$ is the removal treatment effect,and  $\beta$ is the coefficient that 
represents the effect of log genet size, $u$, on survival. 
$W_{ijm,t}$ is the crowding of individual $i$ in species $j$ by neighbors of species $m$ (explained below), and 
$\omega_{jm}$ is an interaction coefficient which determines the impact of crowding by species $m$ on the focal species $j$.

@@

Our model includes crowding from the four dominant species, \textit{A. tripartita}, \textit{H. comata}, \textit{P. spicata}, and \textit{P. secunda}, as well as two covariates representing total crowding from (1) all other perennial grasses and shrubs, which were mapped as polygons, and (2) all forb species, which were mapped as points.

@@

To quantify the short-term population-level consequences of removals, we used an IBM to project the cover of each species in each quadrat one year ahead using versions of the model with and without removal treatment effects. Our models tended to under-predict population growth (Fig. \ref{fig:CoverChange}) and population size (Fig. \ref{fig:IBM1step}) for all species, but the difference between predictions from the baseline and removal models varied among species. For \textit{A. tripartita}, both observed and predicted population growth rates were close to zero, and differences in predictions from the two models were small. \textit{H. comata} experienced greater variation in growth rates, but the inclusion of removal treatment effects had little effect on population growth rates. For \textit{Poa secunda} and especially \textit{P. spicata}, the model with removal effects consistently predicted higher population growth than the baseline model  and reduced the underestimates of cover (Fig. \ref{fig:IBM1step}). Viewing all annual growth rates across species and years shows the same pattern of underprediction for some species, but also reveals a strong correlation between observations and predictions in control plots (Fig. \ref{fig:ObsPred1to1}A). In removal plots, underprediction of growth rates in certain years was larger, especially for \textit{H. comata} and \textit{P. spicata}; including removal treatment effects only slightly reduced this bias (Fig. \ref{fig:ObsPred1to1}B). For the version of the model with maximum removal treatment effects (removal coefficients set to the 95\% confidence limit furthest from zero), the patterns were qualitatively similar, with a somewhat greater contrast between predictions of the baseline and removal models for \textit{P. secunda} and \textit{P. spicata} (Figs. \ref{fig:IBM1step-maxCI},\ref{fig:ObsPred1to1-maxCI}).

 \begin{figure}[tbp]
 \centering
 \includegraphics[width=1\textwidth]{cover_projections_1step}
 \caption{Observed and predicted cover for each of the four modeled species. Solid black lines show mean observed cover averaged across control (closed symbols) and removal treatment (open symbols) quadrats. Blue lines and symbols show one-step-ahead predictions from the baseline IBM (no removal treatment coefficients), averaged across quadrats. Red lines and symbols show one-step-ahead predictions from an IBM that includes removal treatment coefficients. Source file: \texttt{ibm\textbackslash summarize\textunderscore sims1step.r}. }
 \label{fig:IBM1step}
 \end{figure}

  \begin{figure}[tbp]
  \centering
  \includegraphics[width=1\textwidth]{cover_change_1to1}
  \caption{Comparison of observed and predicted annual per capita growth rates across species in (A) control and (B) removal treatments. The black line is a 1:1 line. Solid symbols correspond to predictions from the baseline IBM (no removal effects) and open symbols in (B) show predictions from an IBM that includes removal treatment effects. Source file: \texttt{ibm\textbackslash summarize\textunderscore sims1step.r}. }
  \label{fig:ObsPred1to1}
  \end{figure}

@@

\setcounter{page}{1}
\setcounter{equation}{0}
\setcounter{figure}{0}
\setcounter{section}{0}
\setcounter{table}{0}
\renewcommand{\theequation}{SI.\arabic{equation}}
\renewcommand{\thetable}{SI-\arabic{table}}
\renewcommand{\thefigure}{SI-\arabic{figure}}
\renewcommand{\thesection}{Section SI.\arabic{section}}

\centerline{\Large \textbf{Supporting Information }}
\centerline{Adler et al., ``Weak interspecific interactions''}

@@

\section{Supplementary Methods} \label{suppMethods}

\subsection{Interspecific covariance in local crowding} 
We explored interspecific covariance in local crowding experienced by individual plants, by regressing the $W$ values exerted by one neighbor species, the response variable, against the $W$ values of all other species, the independent variables. Because some $W=0$, we conducted two separate regressions. First, using all $W$'s, we fitted a generalized linear model with a logit link function to evaluate whether the probability that the focal species' $W=0$ is influenced by the value of other species' $W$'s. In this model, the dependent variable is a Bernoulli variate coding for the zero or non-zero value of the focal species' crowding, and the independent variables are the $W$'s for all other species. Second, for the set of records in which the focal species has $W>0$, we performed a linear regression, where the focal species' $W$ is the dependent variable, and the other species' $W$'s are the independent variables. We repeated these regressions for each focal species. Due to large samples size, interspecific $W$ values were often statistically significant predictors of intraspecific. However, they explained very little variance. The maximum reduction in deviance for the generalized linear regressions and $R^2$ for the linear regressions were both less than 8\%. The \texttt{R} code for this analysis is included as ..\texttt{\textbackslash Wdistrib\textbackslash exploreSurvivalWs.r}.

\subsection{Mean field approximation of local crowding for the IPM} 
\citet{adler_coexistence_2010} developed a mean field approximation for local crowding when the
competition kernels are all Gaussian functions, $F_{jm}(d) = e^{-\alpha_{jm} d^2}$. The approximation is explained in 
the online SI to \citet{adler_coexistence_2010} and in section 5.3 of \citet{Ellner2016}. 
Here we explain how that approximation was modified for the IPMs in this paper, which
used fitted nonparametric competition kernels.

@@

\clearpage 
\newpage  
\section{Additional Tables}

@@

\section{Additional Figures}

@@

   \begin{figure}[tbp]
   \centering
   \includegraphics[width=1\textwidth]{cover_change_1to1_maxCI}
   \caption{Comparison of observed and predicted annual per capita growth rates across species in (A) control and (B) removal treatments assuming maximum effects of removals. The black line is a 1:1 line. Solid symbols correspond to predictions form the baseline IBM (no removal effects) and open symbols in (B) show predictions from an IBM that includes removal treatment effects. Source file: \texttt{ibm\textbackslash summarize\textunderscore sims1step.r}. }
   \label{fig:ObsPred1to1-maxCI}
   \end{figure}

>>>>

\section*{Abstract}

A previous study of four dominant species from a sagebrush steppe community used historical data sets and multispecies population models to demonstrate weak interspecific interactions. The models predict little competitive release following species removals. We conducted a removal experiment to test our model's ability to predict the outcome of interspecific interactions. We established new quadrats in the same location where the historical data were collected. We assigned half the new quadrats to a  perennial grass removal treatment and half to a treatment in which we removed the dominant shrub, \textit{Artemisia tripartita}. We modeled survival, growth and recruitment as functions of local neighborhood species composition along with an indicator variable for removal treatment. If our ``baseline" model, which accounts for local plant-plant interactions, explains responses to removal, then the fitted removal indicator effect should be non-significant. For survival and recruitment, the removal treatment effects were never significantly positive, indicating that competitive effects were not underestimated by the baseline model. For  \textit{Poa secunda} recruitment, the removal treatment was actually negative, indicating that our baseline model overestimated competitive effects. For growth, the removal treatment effect was significant and positive for two species, \textit{Poa secunda} and \textit{Pseudoroegneria spicata}, indicating that the baseline model underestimated competitive effects. However, including information about the location of these grass individuals with respect to removed \textit{A. tripartita} failed to improve the growth regressions, raising questions about the mechanisms driving the positive response to removal. For three species, individual based models and integral projections models based on the vital rate regressions showed that removal treatment effects had little impact on population growth rates or simulated equilibrium cover following a species removal. For \textit{P. spicata}, the population models that included effects of \textit{A. tripartita} removal projected greater competitive release than the baseline models. The ability of models based on observational data to predict population responses to experimental removals increased our confidence that competitive release is in fact small for at least three of our four study species. The implication is that interspecific resource competition is not a primary factor determining the structure and dynamics of this community. The success of the models also supports the use of multispecies models, based on long-term observational studies, to characterize competitive interactions in a community.

@@

Stable coexistence requires that intraspecific interactions must limit populations more than interspecific interactions \citep{chesson_mechanisms_2000}.  Whenever we study populations of species that appear to be coexisting stably, such as populations that have co-occurred in close proximity for extended periods, we should expect intraspecific limitations to be stronger than interspecific limitations. However, we still might expect interspecific interactions to be strong and negative. In fact, plant community ecologists often motivate research on coexistence by noting that all plant species compete for water, light, and a few mineral resources (e.g. \citealt{silvertown_plant_2004}). Resource competition plays a central role in both Tilman's mechanistic resource competition models \citep{tilman_resource_1982} and Grime's Competitor-Stress tolerator-Ruderal strategies \citep{grime_plant_1979}. Neutral theory \citep{hubbell_unified_2001} goes even further, assuming that interspecific competition is exactly as strong as intraspecific competition. Although a growing list of studies has emphasized the role of interspecific facilitation in some plant communities \citep{he_global_2013,brooker_facilitation_2008}, it is unclear whether this research has overturned the default assumption that plants compete intensely with other species.

@@

An alternative approach to studying competitive release is to fit multispecies population models that estimate species interactions using long-term, observational data, and then simulate population responses to removals. Applying this approach to arid and semiarid plant communities, we found evidence of strong intraspecific limitation and weak interspecific interactions, leading to very stable coexistence and implying little competitive release \citep{adler_coexistence_2010,chu_large_2015}. In fact, at our sagebrush steppe study site  \citep{adler_coexistence_2010}, our model predicts removal of sagebrush would actually decrease the equilibrium cover of the three dominant grass species by 0.8 to 5.5\%, reflecting the facilitative effect of sagebrush on grass recruitment and very weak competitive effects on growth and survival.  Since we only studied the most common, co-occurring species, we expected to find evidence of stable coexistence, but the predicted negative effect of sagebrush removal on grass cover is surprising given the long history of sagebrush eradication to increase grass forage production in sagebrush rangelands \citep{Cook1963, Mueggler1958, Robertson1947}. Compared to traditional field experiments, our approach has the advantage of projecting full life-cycle responses over long time periods, but its reliance on observational data sets limits the strength of our inference. We would have more confidence in our model's projections of competitive release if we could experimentally confirm the ability of our models to describe interspecific interactions.

To test whether our sagebrush community model, which is based on observational data, underestimates the strength of interspecific competition and competitive release, we conducted a removal experiment in a sagebrush steppe. We studied the responses of three perennial grass species to removal of sagebrush, and the response of sagebrush to removal of all grasses. The primary purpose of the experiment was not to directly measure competitive release, which is difficult to do over a short time period in a semiarid ecosystem with low and variable plant cover, but rather to validate the parameters in our model that represent key interspecific interactions and ultimately determine the magnitude of competitive release. We addressed two research questions: First, are the survival, growth or recruitment of our target species significantly different in control vs. removal treatments after accounting for differences in local species composition? Because our demographic models include the effects of neighborhood crowding, they should be able to predict how experimental removal of neighbors alters demographic performance. If the full effect of experimental removals is stronger than predicted, it means that our statistical models underestimate competitive release.  Our second question integrates across the full life cycle: how do short and long-term population-level responses to removals compare to projections from multispecies population models based on observational data? If models based on observational data adequately describe facilitative and competitive interactions, the population dynamics they project should be similar to projections from models that include information from the experimental removal treatments, a result which would validate the use of models and long-term data sets to study interspecific interactions.

@@

Although the primary focus of our analysis is comparison of observed removal responses with responses predicted by our population models, we also conducted a more traditional statistical analysis of differences in cover trends on control vs. removal plots. The response variable for this analysis was year-to-year change in cover at the quadrat scale, calculated as $log(Cover_{t+1}/Cover_t)$. We tested for the effect of removal treatment on this measure of cover change with a linear mixed effects model implemented in the \texttt{lme4} package \citep{Bates2015} of R, including year and quadrat as random effects. We considered the removal treatment effect to be significant when the 95\% confidence interval on the estimated coefficient did not overlap zero.  Because variance in residuals of plots with low cover was high, we explored fitting by weighted least squares, to account for the apparent heteroscedasiticity. The results of these tests were qualitatively similar, so opted to only report the simpler analysis.

@@

Our regression models for survival, growth and recruitment follow previous work \citep{adler_coexistence_2010,chu_large_2015}. We model the survival probability and the growth of individual genets as a function of genet size, the neighborhood-scale crowding experienced by the genet from both conspecific and heterospecific genets, temporal variation among years, and permanent spatial variation among groups of quadrats (`group'; here means a set of nearby quadrats located within one pasture or grazing exclosure). The current analysis departs from previous work with the inclusion of a categorical removal treatment effect. If the conspecific and heterospecific crowding effects explain demographic rates in removal treatment plots as well as they do in control plots, then there will be no need for the removal treatment effect, and the estimated coefficient will be small and not significantly different from zero. However, if demographic rates in removal plots differ from control plots even after accounting for crowding effects, then the removal treatment effect will be significant. For example, we might find that, holding crowding constant, grasses grow more quickly in the removal plots than in the control plots. This result would indicate that our ``baseline model'', a model including all estimated parameters except for the removal treatment effect, underestimates competitive release. We refer to the model that includes the estimated removal treatment effect as the ``removal model".

More formally, we modeled the survival probability, $S$, of genet $i$ in species $j$ (which is in quadrat group $g$ and removal treatment $h$), 
from time $t$ to $t+1$  as
\begin{equation}
\mbox{logit}(S_{ij,t+1}) = \gamma_{j,t}^S + \varphi_{jg}^S+  \chi_{jh}^S  + \beta_{j,t}^S u_{ij,t} +  
\sum \limits_{m} \omega_{jm}^S {W}_{ijm,t}
\label{eqn:survReg}
\end{equation}
where $\gamma$ is a time-dependent intercept (year effect), $\varphi$ is the coefficient for the 
effect of spatial location group, $\chi$ is the removal treatment effect,and  $\beta$ is the coefficient that 
represents the effect of log genet size, $u$, on survival. 
$W_{ijm,t}$ is the crowding of individual $i$ in species $j$ by neighbors of species $m$ (explained below), and 
$\omega_{jm}$ is an interaction coefficient which determines the impact of crowding by species $m$ on the focal species $j$.

@@

Our model includes crowding from the four dominant species, \textit{A. tripartita}, \textit{H. comata}, \textit{P. spicata}, and \textit{P. secunda}, as well as two covariates representing total crowding from (1) all other perennial grasses and shrubs, which were mapped as polygons, and (2) all forb species, which were mapped as points. Appendix A provides a detailed explanation of how we modeled crowding based on the size of and distance to neighboring plants around each focal genet.

@@

To quantify the short-term population-level consequences of removals, we used an IBM to project the cover of each species in each quadrat one year ahead using versions of the model with and without removal treatment effects. Our models tended to under-predict population growth (Fig. \ref{fig:CoverChange}) and population size (Fig. \ref{fig:IBM1step}) for all species, but the difference between predictions from the baseline and removal models varied among species. For \textit{A. tripartita}, both observed and predicted population growth rates were close to zero, and differences in predictions from the two models were small. \textit{H. comata} experienced greater variation in growth rates, but the inclusion of removal treatment effects had little effect on population growth rates. For \textit{Poa secunda} and especially \textit{P. spicata}, the model with removal effects consistently predicted higher population growth than the baseline model  and reduced the underestimates of cover (Fig. \ref{fig:IBM1step}). Viewing all annual growth rates across species and years shows the same pattern of underprediction for some species, but also reveals a strong correlation between observations and predictions in control plots (Fig. CUT. In removal plots, underprediction of growth rates in certain years was larger, especially for \textit{H. comata} and \textit{P. spicata}; including removal treatment effects only slightly reduced this bias (CUT). For the version of the model with maximum removal treatment effects (removal coefficients set to the 95\% confidence limit furthest from zero), the patterns were qualitatively similar, with a somewhat greater contrast between predictions of the baseline and removal models for \textit{P. secunda} and \textit{P. spicata} (Figs. \ref{fig:IBM1step-maxCI},CUT).

 \begin{figure}[tbp]
 \centering
 %\includegraphics[width=1\textwidth]{cover_projections_1step}
 \caption{Observed and predicted cover for each of the four modeled species. Solid black lines show mean observed cover averaged across control (closed symbols) and removal treatment (open symbols) quadrats. Blue lines and symbols show one-step-ahead predictions from the baseline IBM (no removal treatment coefficients), averaged across quadrats. Red lines and symbols show one-step-ahead predictions from an IBM that includes removal treatment coefficients. Source file: \texttt{ibm\textbackslash summarize\textunderscore sims1step.r}. }
 \label{fig:IBM1step}
 \end{figure}

@@

\setcounter{page}{1}
\setcounter{equation}{0}
\setcounter{figure}{0}
\setcounter{section}{0}
\setcounter{table}{0}
\renewcommand{\theequation}{A-\arabic{equation}}
\renewcommand{\thetable}{B-\arabic{table}}
\renewcommand{\thefigure}{C-\arabic{figure}}
\renewcommand{\thesection}{A.\arabic{section}}

\centerline{\Large \textbf{Appendices}}
\centerline{Adler et al., ``Weak interspecific interactions''}

@@

\section*{Appendix A. Detailed Methods} \label{suppMethods}

\subsection*{Modeling local crowding}

\subsection*{Interspecific covariance in local crowding} 
We explored interspecific covariance in local crowding experienced by individual plants, by regressing the $W$ values exerted by one neighbor species, the response variable, against the $W$ values of all other species, the independent variables. Because some $W=0$, we conducted two separate regressions. First, using all $W$'s, we fitted a generalized linear model with a logit link function to evaluate whether the probability that the focal species' $W=0$ is influenced by the value of other species' $W$'s. In this model, the dependent variable is a Bernoulli variate coding for the zero or non-zero value of the focal species' crowding, and the independent variables are the $W$'s for all other species. Second, for the set of records in which the focal species has $W>0$, we performed a linear regression, where the focal species' $W$ is the dependent variable, and the other species' $W$'s are the independent variables. We repeated these regressions for each focal species. Due to large samples size, interspecific $W$ values were often statistically significant predictors of intraspecific. However, they explained very little variance. The maximum reduction in deviance for the generalized linear regressions and $R^2$ for the linear regressions were both less than 8\%. The \texttt{R} code for this analysis is included as ..\texttt{\textbackslash Wdistrib\textbackslash exploreSurvivalWs.r}.

\subsection*{Mean field approximation of local crowding for the IPM} 
\citet{adler_coexistence_2010} developed a mean field approximation for local crowding when the
competition kernels are all Gaussian functions, $F_{jm}(d) = e^{-\alpha_{jm} d^2}$. The approximation is explained in 
the online SI to \citet{adler_coexistence_2010} and in section 5.3 of \citet{Ellner2016}. 
Here we explain how that approximation was modified for the IPMs in this paper, which
used fitted nonparametric competition kernels.

@@

\renewcommand{\thesection}{B.\arabic{section}}

\section*{Appendix B. Supplementary Tables}

@@

\renewcommand{\thesection}{C.\arabic{section}}

\section*{Appendix C. Supplementary Figures}

@@
